\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=blue,
}

% add tabular command

\newcommand{\btab}[2]{
  \bgroup
  \def\arraystretch{#1}
  \begin{tabular}{#2}
}

\newcommand{\etab}{
  \end{tabular} \smallskip
  \egroup
}

\name{Dylan Johnson} % Your name
\address{166 A Street \\ Salt Lake City, Utah 84103 \\ May, 2022} % Your address
\address{(501)~$\cdot$~547~$\cdot$~1621 \\ dylanatasmsa@gmail.com} % Your phone number and email

\begin{document}

% Work Experience
\begin{rSection}{Experience}

  \begin{rSubsection}{SATCOM and Special Programs, L3Harris}{June 2018 - Present}{Software Engineer}{Salt Lake City, Utah}
  \item Performed software engineering duties for a variety of military comms programs at L3Harris Technologies. 
  \item Responsibilities include the following: development of large and complex C++ projects, assisted with the operation of the team DevOps system, performed extensive linux system administration tasks, TCP/IP socket programming, and played a central role in helping other teams learn how to use Docker and Kubernetes. 
  \item Experience interfacing directly with the customer as well as program primes and subcontractors. 
  \item Current software lead for the L3Harris RASOR Program. I was involved in the development of the RASOR system software from the very beginning; I helped define software requirements and architecture for every major component of the RASOR system software and personally supervised development with agile methodologies. I also provided technical assistance to teams that are integrating with or using RASOR in their pursuits. Daily tasks included software development, providing assistance to new engineers on the program, interfacing with the systems engineers, defining requirements, and EVMS reporting.
  \item Developed most of the code for the ATOLL (Automated Tactical Optical Line of sight Links) program during its initial phase. Worked closely with the software lead and systems engineers to accomplish the goals of the program; this meant that I quickly developed broad knowledge of how the system would operate and had a deep knowledge of the software. Made extensive use of C++ 11 and C++ 14 to develop efficient and bug free code. 
  \item I was also sent to customer visits for the ATOLL program. This involved working with government engineers to test and verify the proper operation of the ATOLL system, feed customer change requests to my software lead, and report bugs. 
  \item I was initially tasked to do C++ and Docker development on the Cypher program; however, I had to take on linux system administration and devops roles when the pandemic forced our devops engineer to work from home. In addition to my normal software development duties, I ensured that the air-gapped lab network remained functional, managed yum and docker repositories, built cross-compilation toolchains, managed git repositories, and helped other engineers learn how to use Docker and Kubernetes, and worked with many teams from different locations during integration events. 
  \item Possesses an active SECRET security clearance.
  \end{rSubsection}
  
  \begin{rSubsection}{Platform Group, Ancestry.com}{March 2017 - May 2018}{Software Developer}{Lehi, UT}
  \item Assisted teams with migration and trouble shooting in a Docker/Kubernetes environment.
  \item Implemented tools for deployment and resource management in Kubernetes.
  \item Implemented and optimized tools for logging and monitoring in Kubernetes.
  \item Stayed current with the latest features in Kubernetes to optimize our current system and add new abilities to developers. 
  \end{rSubsection}
  
  \begin{rSubsection}{Infrastructure as a Service Team, Ancestry.com}{February 2016 - March 2017}{Software Engineering Intern}{Lehi, UT}
  \item Assisted teams with migration and trouble shooting in a Docker/Kubernetes environment.
  \item Implemented tools to ease deployment and resource management in Kubernetes.
  \item Implemented and optimized tools for logging and monitoring in Kubernetes.
  \item Stayed current with the latest features in Kubernetes to optimize our current system and add new abilities to developers.
  \item Helped reimplement a core backend service in Go.
  \end{rSubsection}

  \begin{rSubsection}{Search User Interface Team, Ancestry.com}{May 2015 - February 2016}{Software Engineering Intern}{Provo, UT}
  \item Worked under the SearchUI team of Ancestry.com, and other teams when necessary.
  \item Assisted with the development of new production level code, improved site performance, and fixed bugs.
  \item Contributed to the development of new services and features, such as the pagination widget.
  \item Development in JavaScript, C\#, SQL, Visual Studio 2013, Windows 7.
  \end{rSubsection}

  \begin{rSubsection}{Emerging Analytics Center, UALR}{October 2014 - May 2015}{Software Engineering Intern}{Little Rock, AR}
  \item Worked under Dr. Carolina Cruz-Neira, the inventor of the CAVE system.
  \item Used Unity 3D C\# for 3D programming and model manipulation.
  \item Used OpenCV (used OpenCvSharp to integrate with C\#) for computer vision applications.
  \end{rSubsection}

  \begin{rSubsection}{Search User Interface Team, Ancestry.com}{June 2014 - August 2014}{Software Engineering Intern}{Provo, UT}
  \item Worked with a team of engineers to remove and update an old and restrictive codebase.
  \item Used C\#, ASP.NET MVC3, Microsoft SQL Server, Visual Studio 2012, Team Foundation Server, Windows 7 to develop software.
  \item Used the SCRUM agile software development framework.
  \end{rSubsection}

\end{rSection}

% Education Section

\begin{rSection}{Education}

  \begin{rSubsection}{Utah Valley University}{August 2015 - December 2017}{Graduated with B.S. in Computer Science: Computer Science emphasis and Mathematics Minor}
  \item GPA: 3.65
  \item Courses: Compiler Construction, Computer Networking, Advanced C++, Numerical Programming, Python, Statistics, Analysis of Programming Languages, Advanced/High Performance Architecture, Object Oriented Design Patterns, Ordinary Differential Equations, Analysis of Algorithms, Abstract Algebra (Group Theory), Software Foundations (independent study), Modern Algebra (Group Theory and Ring Theory), Artificial Intelligence.
  \end{rSubsection}
  
  \begin{rSubsection}{University of Arkansas, Little Rock}{August 2014 - May 2015}{B.S. in Computer Science (no degree)}
  \item Courses: Language Structure, Computer Systems and Assembly Language, Linear Algebra, Operating Systems, Databases, Theory of Computation.
  \end{rSubsection}

  \begin{rSubsection}{Arkansas School for Mathematics, Sciences, and the Arts}{August 2012 - May 2014}{High School Graduation}
  \item Third place Intel International Science and Engineering Fair project in Materials Engineering at the local level for my research on the optimization of aluminum can camping stoves.
  \item Courses: AP Calculus AB, Calculus 2, Calculus 3, Advanced placement Physics C Mechanics, Advanced Placement Physics C Electricity and Magnetism, Computer Programming 1, Computer Programming 2, Data Structures and Algorithms, Introduction to Web Application Development, Discrete Mathematics.
  \end{rSubsection}

\end{rSection}

\begin{rSection}{Technical Strengths}

  {\bf General Programming}

  \btab{1.1}{ l l }
  Currently Used Languages: & C++, Go and Unix Shell Scripting \\
  Experience With: & C, C++, Java, Python, Rust, C\#, Javascript, Go, \LaTeX \\
  Version Control Systems: & Git \\
  CI/CD Systems: & Jenkins \\
  \etab

  {\bf Operating Systems}

  \btab{1.1}{ l l }
  Unix: & Linux (mostly Red Hat Enterprise Linux related distributions) \\
  Virtualization Technologies: & Extensive experience with Docker and Kubernetes \\
  \etab

  {\bf Miscellaneous}

  \btab{1.1}{ l l }
  Qualifications: An active SECRET security clerance
  \etab

\end{rSection}

\end{document}
